---
title: "Carbon intensity with intensegRid"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro-to-carbon-intensity}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Electricity is not made equal and it will have a smaller or greater carbon footprint (or carbon intensity) depending on its source, :

```{r example}
library(intensegRid)

# carbon intensity per electricity source
get_factors()
```

### Carbon intensity for the whole UK
Current carbon intensity
```{r british1}
## carbon intensity for the whole Britain for the current 1/2 hr period
get_british_ci()
```

Current carbon intensity for specified dates 
```{r british2}
## function arguments
start <- "2019-04-01"
end <- "2019-04-07"

get_british_ci(start, end)
```

If you want to understand the exact composition of the UK-wide electricity over time, you can use `get_mix()` function:

```{r mix1}
# electricity composition in the current 30 mins
get_mix()
```

```{r mix2}
# electricity composition for the specified dates
get_mix(start, end)
```

Finally, you can access summarised carbon intensity statistics for the specified dates: 

```{r stats}
get_stats(start, end)
```

Additionally, you can add a `block` argument that will group the statistics by specified-length blocks, for example a block length of 2 (hrs over a 24 hr period) will return 12 items with the average, max, min for each 2 hr block.  
```{r stats2}
get_stats(start, end, block = 2)
```



### Carbon intensity per UK country

This package allows you to access carbon intensity data per UK country, i.e. England, Scotland and Wales (Northern Ireland is not included) with `get_national_ci()`:
```{r national1}
# Current carbon intensity per UK country
get_national_ci()
```

```{r national2}
# Current carbon intensity for England 
# Function also accepts region values: "Scotland" and "Wales"
get_national_ci(region = "England")
```

```{r national3}
# Carbon intensity for all the UK countries for specified dates 
get_national_ci(start = start, end = end)
```

### Carbon intensity in UK regions
The API allows you extract information for UK regions using `get_regional_ci()` function, that accepts `region_id` as a required argument. You can access a handy `region_id` lookup table as a package dataset:
```{r regions_lookup}
regions_lookup
```

For example, let's access the current carbon intensity for London: 
```{r region1}
get_regional_ci(region_id = 13)
```

Similarly to other functions in the package, `get_regional_ci()` also accepts `start` and `end` arguments:
```{r region2}
get_regional_ci(region_id = 13, 
                start, 
                end)
```


### Carbon intensity per postcode

Finally, the API allows you to access carbon intensity data per postcode. However, it only accepts outward postcode, i.e. one or two letters, followed by one or two digits. For example, the following code will access the carbon intensity information for EN2 area for the current 1/2 hr: 
```{r postcode1}
get_postcode_ci(postcode = "EN2")
```

As always, we can pass `start` and `end` arguments to the function to extend the time window: 
```{r postcode2}
get_postcode_ci(postcode = 'EN2',
                start,
                end)
```
