---
title: "intro-to-carbon-intensity"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro-to-carbon-intensity}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

1. national
  * for today
  * for a given date
  * for a given date and time (date, period)
  * for a specifc 1/2 hour period (from = datetime)
  * for a given 24-hr period (forward or past)
  * for a given 48-hr period (forward or past)
  * between different datetimes (start, end) 

2. regional
  * for the current 1/2 hr for all the regions
  * as above, for england
  * as above, for scotland
  * as above, for wales
  * as above, for a specified postcode
  * as above, for a specified region
  * for the next 24 hrs (from a specified datetime)
  * as above, for a specified postcode
  * as above, for a specified region
  * for the next 48 hrs (from a specified datetime)
  * as above, for a specified postcode
  * as above, for a specified region
  * for the past 24 hours
  * as above, for a specified postcode
  * as above, for a specified region
  * for the time beteen the two datetimes
  * as above, for a specified postcode
  * as above, for a specified region

3. stats
  * stats for the period between two datetimes
  * stats per block (defined time intervals) between two datetimes

4. generationmix
  * for the current 1/2 hr
  * for the past 24 hrs (from)
  * between the two datetimes
  

```{r setup}
library(intensegRid)
```

```{r ex1}
### intensity ------------
## function arguments
start <- "2019-04-01"
end <- "2019-04-07"

## 
mydata <- get_intensity(start, end)
str(mydata)
```

```{r ex2}
## 
my_regional_data <- get_intensity(start, end, regional = TRUE)
str(my_regional_data)
```

```{r ex3}
## 
get_stats(start, end)
```

```{r ex4}
## 
get_mix()
get_mix(start, end)
```

```{r ex5}
## 
get_factors()
```

```{r ex6}
## 
get_ci_by_postcode("EN2")
```

```{r ex7}
## 
get_regional_ci("England")
get_regional_ci("Scotland")
get_regional_ci("Wales")
```