---
title: "intro-to-carbon-intensity"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro-to-carbon-intensity}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

1. national
  + for a current 1/2 hour **[no arguments]**
  + for today (date; can be merged with below) **[date = today()]**
  + for a given date (date; can be merged with above) **[date = specified_date]**
  + for a given date and time (date, period) **[date = specified_date, period = specified_period]**
  + for a specifc 1/2 hour period (from = datetime) **[date = specified_date, period = specified_period]**
  +- for a given 24-hr period (forward or past) **[start = date/datetime, end = date/datetime]**
  +- for a given 48-hr period (forward or past) **[start = date/datetime, end = date/datetime]**
  +- between different datetimes (start, end) **[start = date/datetime, end = date/datetime]**

2. regional
  + for the current 1/2 hr for all the regions  **[no arguments]**
  + for the current 1/2 hr, for england  **[country = "England"]**
  + for the current 1/2 hr, for scotland **[country = "Scotland"]**
  + for the current 1/2 hr, for wales **[country = "Wales"]**
  + for the current 1/2 hr, for a specified postcode **[postcode = "SW1"]**
  + for the current 1/2 hr, for a specified region **[region = "13"]**
  * for the next 24 hrs, for all the regions (from a specified datetime) **[date = "xxx"]** 
  * for the next 24 hrs, for a specified postcode **[postcode = "SW1", datetime = "xxx"]** 
  * for the next 24 hrs, for a specified region **[start = date/datetime, end = date/datetime, region = "13"]** 
  * for the next 48 hrs, for all the regions (from a specified datetime) **[start = date/datetime, end = date/datetime]**
  + for the next 48 hrs, for a specified postcode **[start = date/datetime, end = date/datetime, postcode = "SW1"]** 
  * for the next 48 hrs, for a specified region **[start = date/datetime, end = date/datetime, region = "13"]** 
  * for the past 24 hours, for all the regions  **[start = date/datetime, end = date/datetime, region = "13"]** 
  + for the past 24 hours, for a specified postcode **[start = date/datetime, end = date/datetime, postcode = "SW1"]** 
  * for the past 24 hours, for a specified region **[start = date/datetime, end = date/datetime, region = "13"]** 
  * for the time beteen the two datetimes, for all the regions **[start = date/datetime, end = date/datetime]** 
  + for the time beteen the two datetimes, for a specified postcode **[start = date/datetime, end = date/datetime, postcode = "SW1"]** 
  * for the time beteen the two datetimes, for a specified region **[start = date/datetime, end = date/datetime, region = 13]** 

3. stats
  +- stats for the period between two datetimes **[start = date(-datetime), end = date/datetime]**
  +- stats per block (defined time intervals) between two  **[start = date(-datetime), end = date (-datetime), block = 2]**

4. generationmix
  + for the current 1/2 hr **[no arguments]**
  +- for the past 24 hrs (from) **[start = date(-datetime), end = date(-datetime)]**
  +- between the two datetimes **[start = date(-datetime), end = date(-datetime)]**

5. others
  + region lookup - export as data
  

```{r setup}
library(intensegRid)
```

```{r ex1}
### intensity ------------
## function arguments
start <- "2019-04-01"
end <- "2019-04-07"

```


```{r ex3}
## 
get_stats(start, end)
```

```{r ex4}
## 
get_mix()
get_mix(start, end)
```

```{r ex5}
## 
get_factors()
```

```{r ex6}
## 
get_postcode_ci("EN2")
```

```{r ex7}
## 
get_regional_ci("England")
get_regional_ci("Scotland")
get_regional_ci("Wales")
```